% ============================================================================
% Fractal Consciousness: Mathematical Models for Dynamical Mind States
% A Scientific Book
% MindFractal Lab
% ============================================================================

\documentclass[11pt, twoside, openright]{book}

% ----------------------------------------------------------------------------
% Packages
% ----------------------------------------------------------------------------
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{mathtools}
\usepackage{physics}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{xcolor}
\usepackage{tcolorbox}
\usepackage{fancyhdr}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{caption}
\usepackage{subcaption}

% Page geometry
\geometry{
    a4paper,
    left=30mm,
    right=25mm,
    top=30mm,
    bottom=30mm
}

% Colors
\definecolor{fractalblue}{RGB}{30, 90, 150}
\definecolor{fractalred}{RGB}{180, 60, 60}
\definecolor{fractalgold}{RGB}{180, 140, 40}

% Hyperref setup
\hypersetup{
    colorlinks=true,
    linkcolor=fractalblue,
    citecolor=fractalred,
    urlcolor=fractalgold
}

% Headers
\pagestyle{fancy}
\fancyhf{}
\fancyhead[LE]{\leftmark}
\fancyhead[RO]{\rightmark}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% Theorem environments
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

% Custom commands (from macros.tex)
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Pcal}{\mathcal{P}}
\newcommand{\Bcal}{\mathcal{B}}
\newcommand{\Acal}{\mathcal{A}}
\newcommand{\Fcal}{\mathcal{F}}
\newcommand{\vx}{\mathbf{x}}
\newcommand{\vz}{\mathbf{z}}
\newcommand{\vc}{\mathbf{c}}
\newcommand{\vzero}{\mathbf{0}}
\newcommand{\mA}{\mathbf{A}}
\newcommand{\mB}{\mathbf{B}}
\newcommand{\mW}{\mathbf{W}}
\newcommand{\mU}{\mathbf{U}}
\newcommand{\mH}{\mathbf{H}}
\newcommand{\mI}{\mathbf{I}}
\newcommand{\mJ}{\mathbf{J}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\sech}{\operatorname{sech}}
\newcommand{\orbit}{\operatorname{orbit}}
\newcommand{\norm}[1]{\left\| #1 \right\|}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\had}{\odot}
\newcommand{\lyap}{\lambda}
\newcommand{\xstar}{\vx^*}
\newcommand{\zstar}{\vz^*}
\newcommand{\eps}{\varepsilon}
\newcommand{\dP}{d_{\Pcal}}

% Book info
\title{
    \Huge\textbf{Fractal Consciousness} \\[1em]
    \LARGE Mathematical Models for Dynamical Mind States \\[2em]
    \large A Scientific Framework for Nonlinear Psychology
}
\author{
    \Large MindFractal Lab Contributors \\[1em]
    \normalsize \url{https://github.com/Dezirae-Stark/mindfractal-lab}
}
\date{\today \\ Version 1.0.0}

% ============================================================================
\begin{document}
% ============================================================================

\frontmatter

% Title page
\maketitle

% Copyright page
\thispagestyle{empty}
\vspace*{\fill}
\begin{center}
\textcopyright{} 2025 MindFractal Lab Contributors \\[1em]
Licensed under the MIT License \\[2em]
\textit{This is a mathematical and computational framework.} \\
\textit{It is not a clinical or diagnostic tool.}
\end{center}
\vspace*{\fill}
\newpage

% Preface
\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}

This book presents a mathematical framework for modeling consciousness states, mental dynamics, and personality-dependent behavior using nonlinear dynamical systems theory. The core idea is simple: mental states can be represented as points in a state space, and their evolution can be described by deterministic (or stochastic) maps that exhibit rich dynamical behaviors including fixed points, limit cycles, chaos, and fractal basin boundaries.

The framework draws inspiration from:
\begin{itemize}
    \item \textbf{Dynamical systems theory}: Chaos, bifurcations, attractors
    \item \textbf{Computational neuroscience}: Metastability, attractor networks
    \item \textbf{Complex systems science}: Self-organization, criticality
    \item \textbf{Calabi-Yau geometry}: Complex structure, higher dimensions
\end{itemize}

\textbf{Important Disclaimers:}
\begin{enumerate}
    \item This is a \emph{conceptual model}, not a literal theory of brain physics
    \item The ``tenth dimension'' interpretation is metaphorical, providing intuitive language for mathematical constructs
    \item The framework is for research and education, not clinical diagnosis
    \item All code and theory are provided under MIT License for open exploration
\end{enumerate}

We hope this book serves as both a mathematical reference and an invitation to explore the intersection of dynamical systems and consciousness research.

\vspace{2em}
\noindent\textit{The MindFractal Lab Team} \\
\textit{November 2025}

% Table of contents
\tableofcontents

% List of figures (optional)
\listoffigures
\addcontentsline{toc}{chapter}{List of Figures}

% ============================================================================
\mainmatter
% ============================================================================

\include{chapters/01_intro}
\include{chapters/02_base_models}
\include{chapters/03_cy_dynamics}
\include{chapters/04_possibility_manifold}
\include{chapters/05_tenth_dimension_metaphor}
\include{chapters/06_ml_embeddings}
\include{chapters/07_visualization_and_interfaces}
\include{chapters/08_future_work}

% ============================================================================
\backmatter
% ============================================================================

% Bibliography
\chapter*{Bibliography}
\addcontentsline{toc}{chapter}{Bibliography}

\begin{thebibliography}{99}

\bibitem{strogatz2018}
Strogatz, S. H. (2018). \emph{Nonlinear Dynamics and Chaos} (2nd ed.). CRC Press.

\bibitem{ott2002}
Ott, E. (2002). \emph{Chaos in Dynamical Systems} (2nd ed.). Cambridge University Press.

\bibitem{kantz2004}
Kantz, H., \& Schreiber, T. (2004). \emph{Nonlinear Time Series Analysis} (2nd ed.). Cambridge University Press.

\bibitem{tognoli2014}
Tognoli, E., \& Kelso, J. A. S. (2014). The metastable brain. \emph{Neuron}, 81(1), 35-48.

\bibitem{freeman2005}
Freeman, W. J., \& Holmes, M. D. (2005). Metastability, instability, and state transition in neocortex. \emph{Neural Networks}, 18(5-6), 497-504.

\bibitem{chialvo2010}
Chialvo, D. R. (2010). Emergent complex neural dynamics. \emph{Nature Physics}, 6(10), 744-750.

\bibitem{breakspear2017}
Breakspear, M. (2017). Dynamic models of large-scale brain activity. \emph{Nature Neuroscience}, 20(3), 340-352.

\bibitem{mandelbrot1982}
Mandelbrot, B. B. (1982). \emph{The Fractal Geometry of Nature}. W.H. Freeman.

\bibitem{milnor2006}
Milnor, J. (2006). \emph{Dynamics in One Complex Variable} (3rd ed.). Princeton University Press.

\bibitem{hubner2006}
H\"ubner, A., et al. (2006). Calabi-Yau Manifolds: A Bestiary for Physicists. In \emph{String Theory and Fundamental Interactions}. Springer.

\end{thebibliography}

% Index (optional)
\chapter*{Index}
\addcontentsline{toc}{chapter}{Index}
\textit{Index entries would be generated by the \texttt{makeindex} tool.}

% ============================================================================
\end{document}
% ============================================================================
